\pkg{Rgbp}: An R Package for Hierarchical Modeling and Method Checking

### 2013-07-22 jss/article.tex
ack
fix
small change

\subsubsection{Rao-Blackwellized Unbiased estimates of Coverage Probabilities}
Rao-Blackwellization improves accuracy of an unbiased estimator by taking conditional expectation given a sufficient statistic. Based on this idea, we define $E(I_{ij}\vert y_{ij}, A, \beta$), where $A$ and $\beta$ were given at first (see 4.1) and $y_{ij}$ is a sufficient statistic. This expectation is the same as Pr$(\hat{\mu}_{ij, low}\le \mu_{ij} \le\hat{\mu}_{ij, upp}\vert y_{ij}, A, \beta)$, where ($\hat{\mu}_{ij, low}$, $\hat{\mu}_{ij, upp}$) is the $j$-th group's interval estimate on the $i$-th dataset. We can calculate this probability  because we know the distribution of ($\mu_{ij} \vert y_{ij}, A, \beta$) in (\ref{normalpost}). Note that conditioning on $y_{ij}$ is equivalent to conditioning on $\mathbf{y}$ as long as $A$ and $\beta$ are known. Then, we can estimate the first group's coverage probability by $\sum_{i=1}^{500}E(I_{i1}\vert y_{i1}, A, \beta)/500$, which is also unbiased but more accurate than the previous simple estimator.

@@

\begin{CodeChunk}
\begin{CodeInput}
R> pcv <- coverage(p, nsim = 10000)
\end{CodeInput}
\end{CodeChunk}
\begin{figure}[h] 
\begin{center}
\includegraphics[width = 5.5cm]{hospital2.png}
\caption{Coverage plot via method checking}
\label{fig:hospital_coverage}
\end{center}
\end{figure}

In \ref{fig:hospital_coverage} we see two estimated coverage probabilities: a simple unbiased estimate (a blue dashed line) and an Rao-Blackwellized unbiased estimate (a red line). Both lines are indistinguishable from the horizontal line at 0.95 and the estimated overall average coverage rate is 0.950 from the Rao-Blackwellized estimate. This result shows that the interval estimates from the suggested multilevel modeling on this particular dataset have nice repeated sampling property.

@@

\begin{CodeChunk}
\begin{CodeInput}
R> gcv <- coverage(g, nsim = 10000)
\end{CodeInput}
\end{CodeChunk}
\begin{figure}[h] 
\begin{center}
\includegraphics[width = 5.5cm]{school2.png}
\caption{Coverage plot via method checking for 8 schools}
\label{fig:schoolcoverage}
\end{center}
\end{figure}
%TODO: wrong reference. you mean 'As seen in Figure 5' below?
As seen in Figure \ref{fig:schoolcoverage} the desired $95\%$ coverage probability was achieved for each group in this example.

@@

\section[acknowledgments]{Acknowledgments}

\bibliography{bibliography}

>>>>

\subsubsection{Rao-Blackwellized Unbiased Estimates of Coverage Probabilities}
Rao-Blackwellization improves accuracy of an unbiased estimator by taking conditional expectation given a sufficient statistic. Based on this idea, we define $E(I_{ij}\vert y_{ij}, A, \beta$), where $A$ and $\beta$ were given at first (see 4.1) and $y_{ij}$ is a sufficient statistic. This expectation is the same as Pr$(\hat{\mu}_{ij, low}\le \mu_{ij} \le\hat{\mu}_{ij, upp}\vert y_{ij}, A, \beta)$, where ($\hat{\mu}_{ij, low}$, $\hat{\mu}_{ij, upp}$) is the $j$-th group's interval estimate on the $i$-th dataset. We can calculate this probability  because we know the distribution of ($\mu_{ij} \vert y_{ij}, A, \beta$) in (\ref{normalpost}). Note that conditioning on $y_{ij}$ is equivalent to conditioning on $\mathbf{y}$ as long as $A$ and $\beta$ are known. Then, we can estimate the first group's coverage probability by $\sum_{i=1}^{500}E(I_{i1}\vert y_{i1}, A, \beta)/500$, which is also unbiased but more accurate than the previous simple estimator.

@@

\begin{CodeChunk}
\begin{CodeInput}
R> pcv <- coverage(p, nsim = 10000)
\end{CodeInput}
\end{CodeChunk}
\begin{figure}[h] 
\begin{center}
\includegraphics[width = 5.5cm]{hospital2.png}
\caption{Coverage plot via method checking}
\label{fig:hospitalcoverage}
\end{center}
\end{figure}

In Figure \ref{fig:hospitalcoverage} we see two estimated coverage probabilities: a simple unbiased estimate (a blue dashed line) and an Rao-Blackwellized unbiased estimate (a red line). Both lines are indistinguishable from the horizontal line at 0.95 and the estimated overall average coverage rate is 0.950 from the Rao-Blackwellized estimate. This result shows that the interval estimates from the suggested multilevel modeling on this particular dataset have nice repeated sampling property.

@@

\begin{CodeChunk}
\begin{CodeInput}
R> gcv <- coverage(g, nsim = 10000)
\end{CodeInput}
\end{CodeChunk}
\begin{figure}[h] 
\begin{center}
\includegraphics[width = 5.5cm]{school2.png}
\caption{Coverage plot via method checking for 8 schools}
\label{fig:schoolcoverage}
\end{center}
\end{figure}

As seen in Figure \ref{fig:schoolcoverage} the desired $95\%$ coverage probability was achieved for each group in this example.

@@

\section[acknowledgments]{Acknowledgments}
The authors would like to thank Phil Everson and the 2012 class of Stat 324r: Parametric Statistical Inference and Modeling for their valuable inputs.
\bibliography{bibliography}
